National demographic-disturbance relationships and local monitoring both reduce uncertainty in projections of boreal caribou population viability: tools to support monitoring decisions

### 2024-02-23 analysis/paper/supplement.Rmd
in progress
Writing in progress.

resultScenario = "S6"
```

@@

|$N_0$|animals|Initial adult population size.|

@@

@@

```{r figDisturbanceAnthroStatic, fig.cap="Anthropogenic disturbance and monitoring scenarios.", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/distScnscmult6ay3aSf0.png")))

@@

```{r powercmult3ay3aSf0, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbanceAnthroStatic) for for static anthropogenic disturbance scenarios). In these examples there are 3 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult3ay3aSf0.png")))
```

@@

```{r powercmult3ay3aSf1, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure 1 for scenarios in which anthropogenic disturbance increases over time). In these examples there are 3 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult3ay3aSf1.png")))
```

```{r powercmult9ay3aSf1, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure 1 for scenarios in which anthropogenic disturbance increases over time). In these examples there are 9 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult9ay3aSf1.png")))
```

>>>>

resultScenario = "S7"
noBiasResultScenario = "S8"

@@

|$N_0=2000$|animals|Initial adult population size.|

@@

|**Expected value of perfect and sample information**|
|$\psi=\text{viable or not}$|binary|True status of a population.|
|$\alpha=\text{viable or not}$|binary|Assigned population status.|
|$\nu_{\alpha,\psi}=1 \text{when} \alpha=\psi, 0 \text{otherwise}$|binary|Value of classification decision.|
|$x$||Simulated observations from an example population.|
|$\tau$||A disturbance and monitoring scenario.|
|$P(\psi|\tau)$|probability|Prior probability of state $\psi$.|
|$P(\psi|x,\tau)$|probability|Posterior probability of state $\psi$.|
|$EVPI_\tau$||Expected value of perfect information.|
|$EVSI_\tau$||Expected value of sample information.|

@@

```{r figDisturbanceAnthroStatic, fig.cap="Static anthropogenic disturbance and monitoring scenarios.", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/distScnscmult6ay3aSf0.png")))

@@

```{r powercmult3ay3aSf0, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbanceAnthroStatic) for static anthropogenic disturbance scenarios). In these examples there are 3 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult3ay3aSf0.png")))
```

@@

```{r figDisturbanceAnthroDeclining, fig.cap="Declining anthropogenic disturbance and monitoring scenarios.", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/distScnscmult6ay3aSf-1.png")))
```

```{r powercmult3ay3aSfm1, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbanceAnthroDeclining) for declining anthropogenic disturbance scenarios). In these examples there are 3 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult3ay3aSf-1.png")))
```

```{r powercmult6ay3aSfm1, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbanceAnthroDeclining) for declining anthropogenic disturbance scenarios). In these examples there are 6 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult6ay3aSf-1.png")))
```

```{r powercmult9ay3aSfm1, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbanceAnthroDeclining) for declining anthropogenic disturbance scenarios). In these examples there are 9 cows per collared cow in recruitment surveys. See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult9ay3aSf-1.png")))
```

# Sensitivity to unkown bias in recruitment estimates from calf:cow surveys

Adding unknown unknown bias does increase uncertainty, but these increases are not large (compare Figs \@ref(fig:powercmult3ay3aSf1)/\@ref(fig:powercmult3ay3aSf1NoBias) and \@ref(fig:powercmult9ay3aSf1)/\@ref(fig:powercmult9ay3aSf1NoBias)). A key reason for this result is that we assumed the same range of values for the probability of misclassifying adults, and the probability of missing calves (supplement B). Presuming that surveyed groups contain more cows than bulls, and that there is an equal probability of misclassifying cows and young bulls and vice versa, then misclassification errors cause high estimated recruitment. Missing calves causes low estimated recruitment, and together these errors tend to cancel one another out.

```{r powercmult3ay3aSf1, fig.cap="The probability of a correct status assessment with unknown bias in recruitment estimates from calf:cow surveys. In these examples there are 3 cows per collared cow in recruitment surveys, and disturbance increases over time (Figure 1). See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult3ay3aSf1.png")))
```

```{r powercmult3ay3aSf1NoBias, fig.cap="The probability of a correct status assessment without bias in recruitment estimates from calf:cow surveys. In these examples there are 3 cows per collared cow in recruitment surveys, and disturbance increases over time (Figure 1). See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",noBiasResultScenario,"/powercmult3ay3aSf1.png")))
```

```{r powercmult9ay3aSf1, fig.cap="The probability of a correct status assessment with unknown bias in recruitment estimates from calf:cow surveys. In these examples there are 9 cows per collared cow in recruitment surveys, and disturbance increases over time (Figure 1). See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",resultScenario,"/powercmult9ay3aSf1.png")))
```

```{r powercmult9ay3aSf1NoBias, fig.cap="The probability of a correct status assessment without bias in recruitment estimates from calf:cow surveys. In these examples there are 9 cows per collared cow in recruitment surveys, and disturbance increases over time (Figure 1). See Figure 4 for additional details. ", cache=TRUE}
knitr::include_graphics(here::here(paste0("figs/",noBiasResultScenario,"/powercmult9ay3aSf1.png")))
```
